# `r tint` {#int}

#### Abstract {-}

(ref:abs-int)

#### Keywords {-}

(ref:key-int)

## What to read?

The question of what to read is simple to be sure, but in fields of scholarly consumption and production it is nonetheless fundamental. Scholarship is a creative profession where a stock of cultural knowledge forms a greater part of the infrastructure of production than in other fields. This is not to say that other occupations, especially manual ones, lack creativity. It is to say that in such fields knowledge has a limited infrastructure. Whereas the know-how of the brick layer is black boxed in her tools and technology and in the human capital she develops by experience and tacit social learning, for the scholar as bricoleur there exists in addition the distinctively overdeveloped feature of cultural archiving as a universal memory. Except perhaps in outstanding feats of primary research, contributions to scholarship are legitimate to the extent that they have used the archive correctly.

This problem of using the archive, by which we mean all libraries and other organizations that help scholars find published work, is easily expressed by the question, "what to read?" Paradoxically, the overdevelopment of the archive promotes a functional imperative: to the extent that more and more of scholarship is memorable, mechanisms must develop to forget large swaths of intellectual history. A person who studied a random draw from the archive, even a monumental one, would no doubt qualify as an educated person. Professionally, however, they would have answered the question in a tragically wrong way. From the perspective of other scholars, there are right and wrong choices about what to read. Because it is so easy to access scholarly memory, the operative question really becomes "what not to read?"

Though Internet search and self-publishing services, especially video and image based ones, are creating archive-like infrastructure for all occupations, even manual ones, the functions are different. Contemporary Internet repositories provide knowledge as factors of production to anyone who queries them, but many do not purport to be archives in the sense that a historical record of cultural produce is preserved for posterity. They are much more concerned with access to contemporaneous than to historical material, and indeed the particular configuration of the contemporary that sells the most ads ahead of search results. True historical archives of the Internet, such as the Internet Archive or Common Crawl, are not used by the public. Indeed why would they be; they expose the dizzying complexity of the history of the Internet, which, even in only its contemporaneous facet is already overwhelming. The Internet searcher tends to be satisficing, and the search companies have refined their ranking of results to meet their users' search budgets efficiently.

Thus Internet search services perform the function of complexity reduction in their own arbitrary way. They do this without the scholarly paradox of memory, which is that in the university system great pains are made to remember everything just so that the correct material may be forgotten. In the cynical view of professions, scholarship is the encryption of memory by secret sets. A lay seeker approaches the academic archive and at great cost of attention plumbs its depths for enlightenment. Tragically, the archive's complexity dooms her to check out a curriculum so hopelessly tacky that it will only certify her lay status. To be professional is to know what are the tasteful combinations of resources. To be a successful professional is to never have wasted time tasting the bad fruit. Librarians much prefer to help undergraduates because they lack taste. They gifted scholars with access to an immortal memory, and looking the horse in the mouth scholars made rules to protect themselves from the responsibilities of using most of it. In this way a taste for scholarship is the axis sorting the field between education and profession.

So again, how do professional scholars know what (not) to read? What then are the structures that lead scholars new and old to answer the question correctly? How does one know what are the lucrative curricula that can be developed from the archive? There are several formal and informal structures that facilitate and compel scholars to make the same choices about what to read. An obvious one is the supposed normative isomorphism of graduate program syllabi, yet it is a common concern that the quality of these are variable. Universities tend to grant great autonomy to professors in writing syllabi, who in the course of their professional travails may not be given opportunities to read what they want. In being forced to carve out time with subordinates, faculty are caught between personal indulgence and a more or less strongly felt fiduciary responsibility to set students on the correct path. If we have less than perfect faith in the strength of educational ethics among faculty, then we should expect that among graduate syllabi are many lists of what not to read. Students who trust too much in the formal curriculum may be lead astray, and even without trust, they may still be left ignorant of where to invest their labor.

In each program there then must be a hidden curriculum of higher quality. The argument of this study addresses the question of where such a curriculum could possibly come from. The provisional answer is that in the informal spaces of graduate programs knowledge of scholarly genre is learned from extracurricular engagement with professional conferences. It is in conference programs that the tacit rules of academic genre are learnable. These genres form the first parsing of the archive for neophytes. Indeed at the most generic level graduate students, if they are confident enough to locate themselves quickly enough, develop a taste for what not to read. If they can do so early on in their careers, they will be armed with the stereotypes necessary to stop reading the wrong and start reading the right material. While this is not enough certainly to make a cleric of a lay worshiper, it is a necessary first step.

### Genre

I take genre as a candidate explicans for the ability of scholars to know what to read and what to avoid from the cultural archive. A theory of genre will benefit from a review of the literature, yet to do so would catch me in the conundrum of performing the phenomenon I wish to explain. The genre structure of sociology should guide me to a definition of genre, a statement that already presumes an ontological difference and morphological relation between disciplines and genres, namely that scholarly genres are not equivalent to scholarly disciplines and that the former are located within the later. I will begin with an unstudied attempt to tease out the relation of discipline and genre before turning to a more rigourous, even empirical, treatment of genre as a term in American scholarship.

Genre is a loanword from French. The origin of the French-Latin word "genre" and the English-German word "kind" both mean membership by inheritance of innate class characteristics, archaically by presumptive blood descent within a family, race, or nation. In common English it is restricted to mean a broad category within art, music, literature, and some but not all other cultural fields (e.g. baseball is not a genre of sports). As a term in scholarship, genre may be an observable phenomenon, a conceptual component of a theory, or a conflation of the two. In the social sciences genre is a specialty concept as in sociology, while in the humanities it is ubiquitous especially in cultural studies. Academics define and use the differently between and within disciplines.

To impose a sociological gloss on the term, these varied uses of genre would make reviewing the literature on the topic difficult, were it not for the discipline structure of the academy. The uses of the term genre are themselves systematically organized by discipline, and a disciple who is adequately trained will know the correct ways to use the term in her local context. To use genre as a disciplinary convention means to first identify your location in the disciplinary field, and then to accept the limitations on scope by excluding those treatments of the term that are extradisciplinary, that is, irrelevant. Disciplinary structure reduces the true cultural complexity of the meaning of genre to a restricted form, which in turn allows humble knowledge workers to engage upon a set of shared assumptions. Such simplicity begets new complexity as disciples spin out the consequences of their local use of genre.

In the sociology of culture, genre is a form of classification enacted by people in various social contexts. In the context of industrial capitalism, genre is an economic principle helping to organize supply and demand within markets for cultural products. There actors see genres among the borders between economic, social, and cultural uses, as a market category helping them acquire or produce content, as a card in proximate games of prestige, or as something to taste, to consume and enjoy directly. Less often genre is knowledge, a component of culture separate from taste, that is a factor in the formation of ideas and skills, whether these lead in turn to economic production or not.

Genre's meaning is context specific and variable across sociological subfields, though it is amplified in empiricist fashion by economy and society approaches that reduce genre to the act of classification itself. I say empiricist because of the empirical ease with which the classification or labeling actions are observed. Especially with Internet distribution systems, it becomes trivial for corporations to observe when a consumer labels her preferences while browsing a content catalog; it is much harder to observe the ideas that consuming a particular piece of content sparks in the mind.

In cultural studies genre is used much differently and much more in accordance with its etymology. To the humanist, genre is an ontological phenomenon, which is to say, genres are differentiated from each other by combinations of discrete features of signs and signifieds. Humanists are trained to establish these ontologies through methodological readings of texts and through cultivation of theories of genre types. These methods are at the same time empirical and interpretive, because in consuming objective texts the researcher actually observes the ideas that form in her own consciousness, and they may hope that others have a resonant experience. Genres have more substance to them for humanists than they do for sociologists. For sociologists of culture, genres are how people use genre labels, while for humanists, genres are knowledge.

As we have said, the meaning of genre for a sociologist of culture is economistic, at the same time a market category and a taste configuration for consumers. The term differs for a sociologist of knowledge, and perhaps for a cultural sociologist. It is ontology as it is for the humanist, however it is not the ontology as represented to the researcher in the consumption of texts. It is the hopelessly unobservable distribution of ontologies appearing in a population of consumers attending to similar texts. The sociologist of knowledge accuses the sociologist of culture of reducing internalist concepts, thought and experience, to externalist ones, taste and preference. The sociologist of culture rejoins, show me proof, and on and on the interlocutors spin around the axis defining the boundary between their subfields.

But this description of subdisciplinary differences really is just an example of a structural theory of genre that is within scope for the sociologist of knowledge and beyond it for the sociologist of culture, due to their epistemological differences. If genres are ontological, then they deeply structure a person's experience of reality. Ontologies form basic perceptual categories, and people with different ontologies of an object experience different things even if oriented to the same objective phenomenon. A ontological theory of genre would, for example, attempt to explain differences in taste as differences in phenomenological perception, whereas a taste theory of genre treats consumption behavior as revealing preferences whose downstream consequences are then explored.

Yet for all the differing treatments of genre mentioned above, do these views of really contradict, or are they in fact complementary? Does genre as distribution serve the economic sociologist's goals, or does a lack of ontological substance lead her astray? Does genre as knowledge remain hopelessly unverifiable, or are theoretical constructs necessary to achieve a correct interpretation of facts? Is everyone at the club listening to the same song hearing the same thing?

## Discipline

To return to disciplines, answering such questions would put the researcher in an adisciplinary predicament, for it would mean eschewing the scope restrictions cherished by disciples. The challenges of a meta-disciplinary analysis are manifold and uncertain. One is as likely to grow her audience as to lose it altogether. She risks the dilettantism of a jack-of-all-trades. What's worse, she exposes herself to a dizzying scale of content to consider. If disciplines are indeed functional, then the meta-analysis that effaces disciplines risks being dysfunctional. The upside, however, is appealing. If the universe of meanings given to the term genre does contain complementary uses, a meta-analysis will allow one to consider the consequences of the now arbitrary segregation of a superior metaconcept across disciplinary boundaries. Both sides of the divide could be strengthened by a cultural exchange of their respective terms. The redundancy of parallel discovery can be avoided.

Pathologies of disciplinarity can be diagnosed and treated. Disciplines are social substructures embedded in a larger society and culture. If disciplinarity is a kind of controlled ignorance exchanged for access to secret knowledge. The wayward uses of a term like genre are always lurking at the edges of the firelight defined by a particular disciplinary camp. Discipline as rigor instructs disciples to resist flirtations with the available complexity of the term. The essential tension is very rarely between what is known and unknown; rather it is more commonly between what is known "here" versus what we are conditioned to be willfully ignorant of "there".

In a motivation of some of the arguments to follow, I take a metadisciplinary approach, which is to cast as wide a net as possible on the term genre. In so doing I hope to test the tacit cultural assumption that discipline-based decisions of relevance are valid, that is, that when we exclude arguments from other disciplines we remove distractions and focus on what is important. The alternative possibility is that we are wasting intellectual resources, because to exclude important work about our topic, even if it is codified in foreign terms, is to risk ignorance and redundancy. The topic is genre and how disciplinary boundaries form such that people using the same word nonetheless cannot communicate effectively. They draw on different paradigms, which is to say the term is not really the same term. What I hope to do is uncover the knowledge contexts surrounding the terms, and map these contexts in a way that enumerates the various communities of discourse and theories constituting the term.

As I have said, the first consequence of eschewing disciplinary limitations is to bloat the size of the "literature" on genre, since no uses of the term would be excluded. An empirical approach to the standard academic convention of a literature review will help reign in the scale and complexity of the task. My aim, however, remains practical rather than scientific. The methods need to be good enough to yield results that offer something new above a traditional literature review relying on library search and disciplinary wisdom about what is important. This is not because a scientific approach is undesirable, it is that it is not yet demanded of "the literature". Sociologists are not expected to take a sociological orientation toward the history of their fields. Rather the literature review serves the social purpose of taking a position in a field of cultural production. It is a listing of a roster of political support and rivalry, and an advertisement to attract a desired audience.

To take an empirical approach to the literature review would be subversive were it not the first 

## Method


### Distant sampling

The methodological premise of a meta-analysis of genre is that the Gordian knot of global cultural complexity can be cut by stratified sampling. I use a large digital archive of texts, JSTOR, to define the cultural universe, and a simple term search of the keyword "genre" to define a sampling frame. I could then take a simple random sample of texts, analyze how each uses the term genre, develop a classification scheme, and enumerate the different uses of the term. Unfortunately, a small sample in a statistical sense may be larger than a poor researcher can handle. 1,000 texts is not large statistically, but it is huge from a content analysis perspective. What's worse, 1,000 texts may still exclude, by random chance, small subcultures of the term. Stratification resolves this issue by delineating those subcultures so none would be left out.

Alas, the JSTOR digital archive lacks subject labels at the article level, though it does include them for book chapters and for journals. While not foolish, inheriting a journal label to the articles included within it may be a coarse approximation if within-journal content variation exceeds between-journal variation. We can use text analytic classification methods to cluster articles directly and discover latent groups of articles, and in so doing we can have an independent standard to compare to the discipline labels given to journals. It is an open question whether such methods align with what we have discussed above as disciplinary and subdisciplinary groupings, for us whether regularities in vocabulary correspond to regularities in the meaning of the term genre. If they do not, then the study will only be a stop en route to a true census of the uses of the term genre, and the contribution will be to have interrogated the quality of the methods used, though this would be a small consolation indeed!

The choice in computational text analysis (CTA) about how to represent texts as data hinges on whether word order is preserved. The older and more tested approach is to not preserve word order. The name given to this "bag of words" format reminds one of its inelegance. A bag of words is a frequency table for each document counting up the number of times particular words are used, a representation that effectively reduces a text to its vocabulary. It is the analyst's crude operational decision to treat vocabularies as indicators of meaning, but social scientists conventionally insist on cross validation via qualitative analysis. While the ambitions of computational text analysis may start with a replacement of, for instance, the standard literature review, the conventional distrust, at least in sociology, of mathematical models of text makes CTA more of a sampling method than an analytic method. The study will culminate in a reading of texts, albeit one that is different than traditional qualitative analysis because the CTA researcher welcomes the introduction of interpretive bias from an understanding of the mathematical model before, during, or after the texts are read. In the game of "choose your influence", CTA is one choice while disciplinary wisdom is another.

There are two types of classification methods in text analysis, direct document clustering and topic modeling. Direct document clustering treats the bag of words as a vector space and calculates distance or similarity metrics between documents, which are then clustered. In a topic model, the relationship between documents is mediated by an unobserved but latently modeled representation of their content; documents are similar because they are formed from the same topics.

Whichever approach one takes, and both may be used, recall that the goal is to organize the texts into strata for the purpose of stratified sampling. We said that we wish to typify and enumerate the different uses of the term genre. By qualitative analysis, we could read every text in a simple random sample and come up with a theory of the use of genre in that text. The demerits of this approach are several [c.f. @Nelson2017Computational\:5]. It would take longer than we want even for too small a sample. We are not humanists and have not been trained in text analysis (this will hound us no matter what). Fatigue will set in, and accuracy and consistency will suffer. We may limit our set of theories to spare us the agony of complexity. It will be hard to reproduce our results. There may be path dependency with a different reading order producing different theories. On the upside, we would be more educated for it.

Instead, we will stratify the sample, and it is in the configuration of the strata that much of the work will be done. The strata impose upon our interpretation of the texts the assumption of sameness. 

### Arms-length reading

The radical (and often maligned) distant reading approach taken by digital humanists is being taken up with gusto by social scientists who are less skeptical of quantitative methods. Following Nelson [*@Nelson2017Computational] I employ a quantitative analysis of texts not replace human reading with machine reading but to support reproducibility in traditional qualitative content analysis. While CTA makes it possible to dispense with reading altogether, knowledge, understanding, and the cultural logics of arguments--especially their ontologies--are still only obtainable by reading primary texts, closely or not. The most radical interpretive CTA method would involve deep neural net supervised machine learning, which may be able to predict how a particular human reader would classify a text without their needing to read it, though this has never been demonstrated. What I gain from CTA is guidance in answering the question of what to read, and perhaps in what order to do so.

As we know, the question of what to read is answered institutionally for scholars already by way of canon, curriculum, word of mouth, and digital reference term search services. These are their own forms of distant reading, because they each make obsolete the archaic image, true of figures like Weber, of a scholar buried in library stacks reading everything they come across (and so it has been said of Weber, forgetting nothing).^[What a scandal it would be if Weber's lionizers discovered that he had only read text indices! Surely they would bury such a fact. But the point would remain that even if a scholar were able to consumer an entire corpus, the sheer scale of contemporary publication is now beyond even a genius's capacity.] These contemporary shortcuts are historically arbitrary, but what is important is first that they serve the function of reducing the overwhelming cognitive complexity of published scholarship, and second structure that reduction in the same way for all scholars. An arbitrary reduction needs to be consistent to act as an infrastructure for subdisciplinary scholarship, otherwise scholars would find themselves located in different literatures.

If distant reading is a criticism of close reading then it has a big hill to climb especially among humanists who are trained to deal methodically with texts very carefully. In the social sciences a type of customary distant reading is that of ritual citations, those that have developed a meaning that may be oblique to their content or at odds with the intentions of the the original authors. A ritual citation is simply one that is cited but not read, but also one that is so often used that its socially acceptable usages are known from other secondary accounts.

What are the social patterns of the traditional literature review are topics for the sociology of knowledge and science and for the information sciences. This is not the task of the current study. What we take from the traditional approach is the consequences of excluding large segments of intellectual history. What CTA makes possible for the first time is a nonarbitrary, inclusive analysis of *all* content in a digitized corpus. It will not necessarily be a good analysis, but what it will lack in quality it will make up for in coverage. A CTA approach to the literature review will at least make clear what lacuna would be left by the traditional approach. They also reduce the potential idiosyncrasy of a particular author's literature review because, unlike a personal reading, a CTA model can be communicated precisely.

Of course the cognitive limitation of how much any scholar can actually read and understand remains. There will be an exclusion mechanism no matter what, therefore a chief assumption of a CTA literature review is that corpus segmentation is both possible and that some reduced form of reading, some sampling procedure, can be said to be representative of the unread portion in each segment. If on the contrary no two snowflakes are alike, then the enterprise of knowing more than we have before is fraught, and CTA becomes yet another arbitrary reducer.

What's worse, or perhaps better, is that there is reason to believe that idiosyncrasy itself is an historically variable feature of disciplines. If institutional isomorphism has proceeded to some high level in contemporary disciplines, then the assumption that reading the bellwether texts is as good as reading the entire herd may hold. If this is true, however, it raises as many questions about the process of institutionalization in cultural production than it answers about the potential to learn truer versions of intellectual history.

## Data

```{r}
library(tm)
library(stm)
library(pbapply)
library(corrplot)
library(slam)
library(igraph)
library(networkD3)
library(fpc)
d<-'?'
strspl<-function(str) {
  x<-gregexpr('[a-z][A-Z]',str)[[1]]
  if(x[1]==-1) return(str)
  x<-c(1,x+1,nchar(str)+1)
  r<-list()
  for(i in 2:length(x)) r[[i-1]]<-substr(str,x[i-1],x[i]-1)
  unlist(r)
}

jart<-fread(input = 'd/d/jstordfr/genre/genre_journal_article_jst_get_article-1.csv')
jbok<-fread(input = 'd/d/jstordfr/genre/genre_book_chapter_jst_get_book-1.csv')[,discipline:=mapply(strspl,str=discipline,SIMPLIFY =F)]
```


```{r}
f<-'d/p/jstordfr-genre.RData'
if(file.exists(f)){
  load(f)
} else {
  library(future)
  plan(multiprocess)
  library(tm)
  
  #dir('d',pattern = '\\.zip$',recursive = T,full.names = T)
  zp<-'d/d/jstordfr/receipt-id-1228331-part-001.zip'
  jst_preview_zip(zp)
  import <- jst_define_import(
    article = c(jst_get_article, jst_get_authors),
    book = c(jst_get_book,jst_get_authors),
    ngram1 = jst_get_ngram
  )
  jst_import_zip(zp,out_file='genre',out_path='d/d/jstordfr/genre',import_spec=import)
  system.time(dfrg<-fread("d/d/jstordfr/genre/genre_ngram1_jst_get_ngram-1.csv"))
  # get rid of docs containing genre fewer than 5 times
  genprp<-dfrg['genre',on='ngram',round(prop.table(table(n))*100,5)]
  setkey(dfrg,ngram,n)
  cul<-dfrg[CJ(ngram='genre',n=1:4),file_name %>% unique]
  setkey(dfrg,file_name)
  dfrg<-dfrg[!.(cul)]
  # get rid of 1 and 2 frequency words, must appear thrice or more in a document, also a lot of ocr errors
  setkey(dfrg,n)
  dfrg<-dfrg[!.(1:2)]
  # get rid of 1 and 2 character words, and unrealistically long terms
  dfrg[,nc:=nchar(ngram)]
  setkey(dfrg,nc)
  dfrg<-dfrg[!.(c(1:2,25:max(nc)))]
  # assuming remaining glyphs are valid terms, compile word count
  wc<-dfrg[,.(n=sum(n)),by=file_name]
  mta<-list(gp=genprp,wc=wc)
  save(mta,file='d/p/jstordfr-genre-mta.RData')
  # process, stem
  system.time(dfrg[,lemma:=ngram %>% removeWords(words = union(stopwords("en"),stopwords("SMART"))) %>% removeNumbers %>% stemDocument])
  # drop empty lemma
  dfrg<-dfrg[grep('[a-z]',lemma)]
  # collapse lemma
  voc<-dfrg[,.(n=sum(n)),by=.(lemma,ngram)][,.(com=ngram[which.max(n)],N=sum(n)),by=lemma]
  dfrg<-dfrg[,.(n=sum(n)),by=.(file_name,lemma)]
  dfrg[voc,on='lemma',com:=com]
  # quick get rid of short lemma
  voc[,nc:=nchar(lemma)] %>% setkey(nc)
  voc<-voc[!.(1:2)]
  voc[,table(N) %>% prop.table %>% head]
  # sparsity, minimum number of docs (6 here)
  # can be done with prepDocuments later
  # setkey(voc,N)
  # voc<-voc[!.(1:5)]
  setkey(dfrg,lemma)
  dfrg<-dfrg[voc$lemma]
  save(dfrg,file=f)
}
rm(f)
```


We will use the JSTOR Data for Research service to download a corpus of texts for topic modeling. I take the following steps to develop a corpus:

1. Search dfr.jstor.org using the query `(ta:genre OR ab:genre) AND la:eng` and requesting 1grams.
1. To cull documents for which genre is not an important term, exclude documents containing the 1gram "genre" fewer than five times.
1. Remove ngrams appearing fewer than three times, which often includes optical character recognition errors.
1. Remove ngrams shorter than three characters and longer than 25 characters, again often OCR errors but also stopwords that will be removed anyway.^[The Freudian "id" is an unfortunate casualty of this step, as well as some footnotes, endnotes, and captions containing small text where word boundaries were not detected during OCR and a series of words was concatenated.]
1. Compile baseline word counts for each document assuming that at this step the documents contain only valid terms, and no OCR errors.
1. Remove SMART stopwords.
1. Remove numbers.
1. Remove punctuation, except intraword hyphens.
1. Lemmatize or stem English words.
1. Remove lemma with fewer than three characters.
1. Aggregate 1grams defined by a single lemma and, for ease of interpretation, name the sum after the most common 1gram.
1. Remove terms appearing in fewer than 20 documents.
1. Remove documents that, after the above filters, have a word count of fewer than 500 words.


The initial query returned `r d` articles from `r d` different journals, as well as `r d` book chapters. After the above processing steps, the sample was reduced to `r d`. It is fair to ask what was lost. While I do not carefully look at the content of the excluded documents, assuming they were not texts that made important use of the term genre, I do retain some information about what components of a text were lost of those documents that were not cut. This is a measure called idiosyncrasy, which I will have cause to interpret later. 

```{r}
f<-'d/p/cull_dfrg.RData'
if(file.exists(f)){
  load(f)
} else {
  cull<-dfrg[.(dfrg['genr',on='lemma',file_name %>% unique]),on='file_name'][,.(gp=sum(n[lemma=='genr'])/sum(n)),by=file_name][,.(file_name,gp,c=pamk(log(gp),krange = 5)$pamobject$clustering)]
  setkey(cull,file_name)
  save(cull,file=f)
}
rm(f)
cull[,hist(gp %>% log,breaks=50)]
cull[,.(gp=min(gp)),by=c]$gp %>% {abline(v=log(.),col='blue')}
```

```{r}
f<-'d/p/genre-stm.RData'
if(file.exists(f)){
  load(f)
} else {
  meta<-dfrg[,.(N=sum(n),gp=sum(n[lemma=='genr'])/sum(n)),by=file_name]
  dfrg[,`:=`(file_name=factor(file_name),com=factor(com))]
  setkey(dfrg,file_name,com)
  stm<-dfrg[,readCorpus(simple_triplet_matrix(i=file_name %>% as.numeric,j=com %>% as.numeric,v=n,dimnames=list(d=levels(file_name),v=levels(com))),type='slam')]
  stm<-prepDocuments(stm$documents,vocab=dfrg$com %>% levels,meta=meta,lower.thresh = 20)
  # remove docs that were trimmed too deeply by above, must have 500 words remaining
  cul<-stm$meta$file_name[sapply(stm$documents,function(x) sum(x[2,]))<500]
  dfrg<-dfrg[!.(cul)]
  dfrg[,`:=`(file_name=droplevels(file_name),com=droplevels(com))]
  stm<-dfrg[,readCorpus(simple_triplet_matrix(i=file_name %>% as.numeric,j=com %>% as.numeric,v=n,dimnames=list(d=levels(file_name),v=levels(com))),type='slam')]
  cat('\n')
  stm<-prepDocuments(stm$documents,vocab=dfrg$com %>% levels,meta=meta,lower.thresh = 20)
  save(stm,file=f)
}
rm(f)
```

```{r}
f<-'lit/genre-mod.RData'
if(file.exists(f)){
  load(f)
} else {
  mod<-pblapply(2:10,FUN = function(k) 
    stmbow2lda.f(stm,out.dir = 'lit',k = k,verbose = F,check.for.saved.output = F,save.to.disk = T) ,cl = 2)
  save(mod,file=f)
}
rm(f)
```

## sankey

Topic models require the analyst to choose the number of topics $K$. The approach we take to guiding this decision is not to expect one correct specification of K but rather to see it as a changing resolution. A K=2 model usefully bifurcates the sample and is not wrong because it is too restrictive. As K increases we expect the samples to continue to divide as new parameter spaces become available to partition the sample. While this is not strictly a hierarchical design, since each K model is fit independently, we should expect to see aspects of hierarchical topics as well as some degree of stability in the relationships among topics.

Categorical Expectation Maximization is known to 

## top x doc
```{r}
el<-lapply(mod,function(x) x$doc.top.theta * x$doc.length)
for(i in 1:length(el)) dimnames(el[[i]])<-list(d=paste0('d',1:nrow(el[[i]])),t=paste0(i+1,'k',1:ncol(el[[i]])))
th<-el %>% unlist %>% sample(1000) %>% {data.table(w=.,c=pamk(.)$pamobject$clustering)[,.(.N,m=mean(w),mn=min(w),mx=max(w)),by=c]}
for(i in 1:length(el)) el[[i]][el[[i]]<=th$mx[which.min(th$m)]]<-0
```

```{r}
bel<-list()
for(i in 2:length(el)) {
  y<-do.call(cbind,el[(i-1):i]) %>% crossprod(.)
  y[lower.tri(y,T)]<-0
  bel[[length(bel)+1]]<-as.simple_triplet_matrix(y) %>% {data.table(s=.$dimnames[[1]][.$i],r=.$dimnames[[2]][.$j],w=.$v)[sub('k.+','',s)!=sub('k.+','',r),.(s,r,weight=w)]}
}
bel<-rbindlist(bel)[,k:=tstrsplit(s,split='k',type.convert = T)[[1]]][,weight:=weight %>% prop.table %>% `*`(100),by=k][,k:=NULL]

# cull a bit, actually better to do before cross prod
# bel[,c:=pamk(weight,krange = 6:10)$pamobject$clustering]
# bel<-bel[c!=bel[,.(w=mean(weight)),by=c][,which.min(w)]][,c:=NULL]
# bel[,k:=tstrsplit(s,split='k',type.convert = T)[[1]]][,weight:=weight %>% prop.table %>% `*`(100),by=k][,k:=NULL]

g<-graph_from_edgelist(bel[,!'weight'] %>% as.matrix)
E(g)$weight<-bel[,weight]
```

```{r}
nid<-merge(bel[,.(wp=prop.table(weight) %>% max),by=s],bel[,.(wp=prop.table(weight) %>% max),by=r],by.x = 's',by.y = 'r')[,k:=tstrsplit(s,split='k',type.convert = T)[[1]]][,c:=pamk(.SD)$pamobject$clustering,.SDcols=ec('wp.x,wp.y')] %>% setkey(s)
nd3<-igraph_to_networkD3(g)
nd3$nodes$group<-nid[.(nd3$nodes$name),c]
nd3$nodes$group[is.na(nd3$nodes$group)]<-0
nd3$nodes$group<-as.character(nd3$nodes$group)

mkg<-function(x) ec(x,'\n') %>% strsplit(',') %>% do.call(rbind,.) %>% apply(2,match,nd3$nodes$name) %>% matrix(ncol=2) %>% `-`(1) %>% data.table %>% setnames(ec('source,target'))

gr<-c(
  '2k2,3k3'
  ,
  '2k2,3k1
3k1,4k3'
,
'2k1,3k2
3k2,4k4
4k4,5k4'
,
'3k3,4k2
4k2,5k2
5k2,6k2
6k2,7k2
7k2,8k2
8k2,9k2
9k2,10k2'
,
'3k3,4k1
4k1,5k1
5k1,6k1
6k1,7k1
7k1,8k1
8k1,9k1
9k1,10k1'
,
'4k3,5k3
5k3,6k3
6k3,7k3
7k3,8k3
8k3,9k3
9k3,10k3'
,
'4k3,5k5
5k5,6k5
6k5,7k5
7k5,8k5
8k5,9k5
9k5,10k5'
,
'5k4,6k4
6k4,7k4
7k4,8k4
8k4,9k4
9k4,10k4'
,
'5k4,6k6
6k6,7k6
7k6,8k6
8k6,9k6
9k6,10k6'
) 
gs<- gr %>% lapply(mkg)
nd3$links<-data.table(nd3$links)
nd3$links[,group:='0']

for(i in 1:length(gs)) nd3$links[gs[[i]],on=ec('source,target'),group:=as.character(i)]

```

```{r,include=T,fig.cap='Sankey diagram of document overlap between topic models of increasing values of K.'}
sankeyNetwork(Links = nd3$links,Nodes = nd3$nodes,Source = 'source',Target = 'target',Value = 'value',NodeID = 'name',NodeGroup = 'group',LinkGroup = 'group',iterations = 5000,nodePadding = 0)
```

```{r}
mem<-list()
for(i in 1:length(gr)) {
  mem[[i]]<-list()
  for(j in gr[i] %>% strsplit(',|\n') %>% unlist) {
    mem[[i]][[j]]<-strsplit(j,'k')[[1]] %>% as.numeric %>% {mod[[.[1]-1]]$doc.top.theta[,.[2]]} %>% order(decreasing=T)
  }
}
rnk<-lapply(mem,lapply,function(x) data.table(d=x,r=length(x):1)) %>% lapply(rbindlist) %>% lapply(function(x) x[,.(r=sum(r)),by=d] %>% setorder(-r))
```

```{r}
url<-rbindlist(list(jart[,.(file_name)],jbok[,.(file_name)]))[,.(file_name,url=paste0('www.jstor.org/stable/',sub('[a-z-]+-','',file_name) %>% sub('_','/',.)))]
stm$meta[url,on='file_name',url:=url]


```

```{r qcv}
withr::with_seed(
  12345,{
    sf<-4:9 %>% combn(2) %>% t %>% {data.table(.)[sample(1:.N)]}
    for(i in 1:nrow(sf)) sf[i,] %>% unlist %>% {c(rnk[[.[1]]][1:25,sample(d,5)],rnk[[.[2]]][1:25,sample(d,5)])} %>% sample %>% stm$meta[.,.(lr='',url,file_name)] %>% write.table(file = paste0('d/p/jstordfr/genre/man',sprintf('%02d',i),'-',Sys.time() %>% as.integer,'.txt'),quote = F,sep = '\t',row.names = F,col.names = T)
  }
)
```

