\documentclass [PhD] {uclathes}

% \input {mymacros}                         % personal LaTeX macros

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Usually things live in separate flies.
%
 \input {preamble}                           % preliminary page info

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                      %
%                          PRELIMINARY PAGES                           %
%                                                                      %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title          {Knowledge of the Social Sciences}
\author         {Brooks Ambrose}
% Note: department is really your area of research.  I.e. leave out 'Department of'.
\department     {Sociology}
% Note:  degreeyear should be optional, but as of  5-Feb-96
% it seems required or you get a year of ``2''.   -johnh
\degreeyear     {2019}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\member         {Gabriel Rossman}
\member         {Jacob Foster}
\member         {Barbara Lawrence}
\chair          {Lynne G. Zucker}
%\chair          {Chair's name 2}
%\chair          {Chair's name 3}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\dedication     {\textsl{To Adena \ldots \\
                my mound builder,
                that you may learn to care
                about who came before
                and who will come after. \\~\\
                To Bill the theorist, \\
                Jean the historian, and \\
                Julia the artist \ldots \\
                I am nothing more \\
                than each of you \\~\\
                To Jessica \ldots \\
                I shall never grow so old again! \\
                (I promise)
                }}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\acknowledgments {
I would like to acknowledge the years of support I have received from many wonderful people. First and foremost I would like to thank my family for supporting my education for just one more decade than they expected. I am happy that you will finally know what I was doing.

Professor Mark Gould of Haverford College introduced me to sociology and helped me feel connected to something much older and bigger than myself. He together with Victor Lidz showed me the importance of a theoretical imagination in the study of history. Any creativity in my use of data is attributable to their creativity in the use of ideas.

Lynne Zucker has been a mentor and a friend. She demonstrates that great intelligence and great kindness take one farther than either could alone. I would not have finished without the courage she inspired. I am honored to share co-authorship of Chapter 4 of this manuscript with her. Her knowledge of data sources and the importance of economic history, as well as her leadership in institutional and organizational theory, helped to turn an interesting project into an important one.

Jacob Foster, Barbara Lawrence, and Gabriel Rossman have provided years of support and guidance. I am eternally grateful for their tireless dedication to their students.

I have the deepest faith in Johann Koehler and know that he will do great things. I will always trust him to care deeply about me and my work.

Peter Norlander invited me to apply for my first faculty position at the University of California, and opened up a new world of opportunities for me as a result.

The colleagues and friends I have met through the D-Lab at the University of California are the source of my fascination with machine reading of texts and my capacity to do something about it. My fellow travelers in the D-Lab Computational Text Analysis Working Group introduced me to most of the methods I use in this manuscript. Without the lessons I learned from Aaron Culich, not to mention the free server time, I could never have cleared the technical hurdles necessary to get the job done. His generosity and dedication to service is truly remarkable.

Yuvi Panda and the Jupyter team at the Berkeley Institute of Data Science invented many of the tools I use on a daily basis. Their hard work is creating opportunities for a new generation of scholars to leverage technology for the greater good.

Thank you Sandra Vizireanu, for letting me work in your vault.

Benjamin Franklin is an American icon that will never be forgotten. His charm, inventiveness, soft heart, and wry wit continue to inspire a nation.

Jessica and Adena are my heart and soul. I cannot wait to spend more time with them.

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%
% UCLA Policy on Vita
% For security reasons, UCLA policy specifies that your birth year and birth place should not be included in your vita.
%
\vitaitem   {2016}
                {Dissertation Year Fellowship, Graduate Division, UCLA.}
\vitaitem   {2013}
                {Ph.D. Candidate in Sociology, UCLA.}
\vitaitem   {2011}
                {M.A. in Sociology, University of California, Los Angeles (UCLA).}
\vitaitem   {2006}
                {B.A. in Sociology, Haverford College, Haverford, Pennsylvania.}
\vitaitem   {2015-2018}
		{Instructor, Master's of Information and Data Science, School of Information, University of California, Berkeley (UC Berkeley).}
\vitaitem   {2015}
		{Graduate Assistant, D-Lab, UC Berkeley.}
\vitaitem   {2014-2015}
		{Organizer, Computational Text Analysis Working Group, D-Lab, UC Berkeley.}
\vitaitem   {2014}
		{Teaching Fellow, Department of Sociology, UCLA.}
\vitaitem   {2012-2013}
		{Teaching Associate, Department of Sociology, UCLA.}
\vitaitem   {2011-2012}
		{Teaching Assistant, Department of Sociology, UCLA.}
\vitaitem   {2013}
		{Research Assistant, Stefan Bargheer, Department of Sociology, UCLA.}
\vitaitem   {2012, 2013}
		{Research Assistant, Patrick Heuveline, Department of Sociology, UCLA.}
\vitaitem   {2009-2014}
		{Recipient, Departmental Fellowship, Department of Sociology, UCLA.}
\vitaitem   {2010-2011}
		{Recipient, Graduate Research Mentorship, Graduate Division, UCLA.}
\vitaitem   {2010}
		{Recipient, Graduate Summer Research Mentorship, Graduate Division, UCLA.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\abstract {
This dissertation contains four studies in the mapping of scholarly knowledge with special reference to the social sciences. Chapter one theorizes three roles within universities, archivists, professionals, and educators, and explains how their collusions and collisions over knowledge as a valued resource shape knowledge terrains over time. Chapter two uses advanced network visualization techniques to model how the assignment of discipline subject labels to journals by digital archivists can be analyzed to reveal an implicit cognitive map of disciplines. Chapter three uses a topic model to conduct an expansive literature review covering thousands of articles to understand what the term genre means in different disciplines, and it invents several diagnostic techniques to validate model quality. Chapter four uncovers the historical origins of social science in the United States from the end of the Civil War until the Great Depression, and it uses a topic model to track the development of the genre structure of anthropology and sociology as each discipline contends with the establishment of the university system and with the dawning of World War I. Together these studies establish an agenda for the systematic cartography of social science knowledge that will help scholars reach a deeper understanding of the history of their fields.
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\begin {document}
\makeintropages
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Ordinarily each chapter (at least) is in a separate file.
%
\input {ambrose_dissertation}                         % Chapter 1 of dissertation
%\input {chapter2}                         % Chapter 2
%\input {chapter3}                         % etc.
%\input {chapter4}
%\input {chapter5}
%\input {chapter6}
%\input {chapter7}
%\input {chapter8}

\bibliography {references}    % bibliography references
\bibliographystyle {thesis}

\end {document}

